Statistical Searches for Microlensing Events in Large, Non-Uniformly Sampled Time-Domain Surveys: A Test Using Palomar Transient Factory Data

### 2013-10-16 text/paper/ms.tex
Added durbin-watson reference

$\eta$, the von Neumann ratio \citep[][also known as the Durbin-Watson statistic]{von_neumann1941}, is the mean square successive difference divided by the sample variance:
\begin{align}
	\eta = \frac{\delta^2}{\sigma^2} = \frac{\sum^{N-1}_i(x_{i+1} - x_i)^2/(N-1)}{\sigma^2}.
\end{align}
$\eta$ is small when there is strong positive serial correlation between successive data points.

@@

\begin{thebibliography}{53}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

>>>>

$\eta$, the von Neumann ratio \citep[][also known as the Durbin-Watson statistic]{von_neumann1941, durbin50}, is the mean square successive difference divided by the sample variance:
\begin{align}
	\eta = \frac{\delta^2}{\sigma^2} = \frac{\sum^{N-1}_i(x_{i+1} - x_i)^2/(N-1)}{\sigma^2}.
\end{align}
$\eta$ is small when there is strong positive serial correlation between successive data points.

@@

\begin{thebibliography}{54}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

\bibitem[Durbin \& Watson(1950)]{durbin50}
J.~Durbin and G.~S. Watson.
\newblock Testing for serial correlation in least squares regression: I.
\newblock {\em Biometrika}, 37(3/4):pp. 409--428, 1950.
